Comparing vector-based and ACT-R memory models using large-scale datasets:\protect\\User-customized hashtag and tag prediction on Twitter and StackOverflow

### 2014-11-24 writeups/dissertation/dissertation.tex
foo

Hashtags for Twitter were both placed at the very end of the Tweet and embedded within the middle of the tweet.
For the popular-hashtags dataset, 11\% of hashtags were the last word in the Tweet and the rest were embedded within the tweet (not at the end).
Tags for StackOverflow were always placed at the very end of the post, since the author chose tags by placing them in a separate text field before submitting the post.

>>>>

Hashtags for Twitter were both placed at the end of the Tweet and embedded within the middle of the tweet.
For the popular-hashtags dataset, 11\% of hashtags were the last word in the Tweet and the rest were embedded within the tweet (not at the end).
Tags for StackOverflow were always placed at the end of the post, since the author chose tags by placing them in a separate text field before submitting the post.
